Distinguishing multiple-merger from Kingman coalescence using two-site frequency spectra

### 2018-11-03 manuscript/manuscript.tex
Fix biblatex in-text citation issue.

\documentclass[11pt, letterpaper]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{url}
% Author affiliations
\usepackage{authblk}
% Allow inline lists
\usepackage[inline]{enumitem}
\usepackage[
    backend=biber,
    citestyle=authoryear,
    style=authoryear,
    autocite=inline,
    isbn=false, doi=false, url=false, eprint=false,
    uniquename=false,
    maxcitenames=2
]{biblatex}

@@

\begin{table}[ht!]
  \begin{center}
    \caption{Boundaries of the homogeneous central regions of chromosomes (shown in \ref{fig:dpgp_pi}).}
    \label{tab:central_regions}
    \begin{tabular}{l|r|r} % <-- Alignments: 1st column left, 2nd middle and 3rd right, with vertical lines in between
      \textbf{Chr.} & \textbf{Start position (MB)} & \textbf{End position (MB)}\\
      \hline
      2L & 1 & 17\\
      2R & 6 & 19\\
      3L & 1 & 17\\
      3R & 10 & 26
    \end{tabular}
  \end{center}
\end{table}

>>>>

\documentclass[11pt, letterpaper]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{url}
% Author affiliations
\usepackage{authblk}
% Allow inline lists
\usepackage[inline]{enumitem}
\usepackage[
    backend=biber,
    citestyle=authoryear,
    style=authoryear,
    autocite=inline,
    isbn=false, doi=false, url=false, eprint=false,
    uniquename=false,
    uniquelist=false,
    maxcitenames=2,
    mincitenames=1,
    maxbibnames=9
]{biblatex}

@@

\begin{table}[ht!]
  \begin{center}
    \caption{Boundaries of the homogeneous central regions of chromosomes (shown in \fig{fig:dpgp_pi}).}
    \label{tab:central_regions}
    \begin{tabular}{l|r|r} % <-- Alignments: 1st column left, 2nd middle and 3rd right, with vertical lines in between
      \textbf{Chr.} & \textbf{Start position (MB)} & \textbf{End position (MB)}\\
      \hline
      2L & 1 & 17\\
      2R & 6 & 19\\
      3L & 1 & 17\\
      3R & 10 & 26
    \end{tabular}
  \end{center}
\end{table}
